Very simplified likelihood

### 2024-08-22 inst/very_simplified_likelihood.Rmd
one parkrun analysis, not two

Above shows that there is no evidence to suggest that the Stirling
strength differs from the Auckland strength.  Now let's try a
logistic-style regression:

@@

# Park run, version 2.

```{r}
a <- read.table("parkrun_results.txt",header=TRUE)

rank_stir    <- a$place  [a$venue == "stirling"]
runners_stir <- a$runners[a$venue == "stirling"]

rank_auck    
runners_auck

rank_stir 
runners_stir

```{r}
support_vec <- function(a,ranks,runners){
    out <- 0
    for(i in seq_along(ranks)){
        out <- out + f_single(a, ranks[i],runners[i],log=TRUE)
    }
    return(out)
}

support_ij <- function(v){
    auck <- v[1]
    stir <- v[2]
    return(
        support_vec(auck, rank_auck, runners_auck) +
        support_vec(stir, rank_stir, runners_stir)
    )
}

x <- seq(from=0.1,to=0.8,by=0.01)
jj <- as.matrix(expand.grid(x,x))
L <- apply(jj,1,support_ij)
L <- L - max(L,na.rm=TRUE)
L <- matrix(L,length(x),length(x))
```

```{r}
parkrun_contour <- function(...){
    par(pty='s')
    contour(x,x,L,asp=1,xlim=range(x),ylim=range(x),levels=-(0:5),xlab="Auckland",ylab="Stirling")
    abline(0,1)
}
parkrun_contour()
```

```{r}
M <- matrix(c(
    sum(rank_auck-1),sum(runners_auck-rank_auck),
    sum(rank_stir-1),sum(runners_stir-rank_stir)),2,2,byrow=TRUE)
dimnames(M) <- list(venue=c("Auckland","Stirling"),better=c(T,F))
M
fisher.test(M)
```

>>>>

Above shows that there is no evidence to suggest that the Stirling
strength differs from the Auckland strength.

## Fisher parkrun

```{r splitruns}
a <- read.table("parkrun_results.txt",header=TRUE)

rank_stir    <- a$place  [a$venue == "stirling"]
runners_stir <- a$runners[a$venue == "stirling"]
```

```{r fisherparkrun}
M <- matrix(c(
    sum(rank_auck-1),sum(runners_auck-rank_auck),
    sum(rank_stir-1),sum(runners_stir-rank_stir)),2,2,byrow=TRUE)
dimnames(M) <- list(venue=c("Auckland","Stirling"),better=c(T,F))
M
fisher.test(M)
```

## Logistic parkrun

Now let's try a
logistic-style regression:

@@
